A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$

### 2025-04-06 paper_v02/article.tex
zig tests
latex time tables

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Fernando Ferraz Ribeiro~\orcidlink{0000-0002-0685-4774}\\Universidade Federal da Bahia
   \And Gilney Figueira Zebende~\orcidlink{0000-0003-2420-9805}\\Universidade Estadual\\de Feira de Santana}
\Plainauthor{Fernando Ferraz Ribeiro, Gilney Figueira Zebende}
%  and $DMC_x^2$
%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$}
\Plaintitle{A Python/Zig optimized and customizable implementation for the Pdcca and DMCx2 methods}
\Shorttitle{\proglang{Python}/\proglang{Zig} implementation for the $\rho_{DCCA}$ and $DMC_x^2$}

@@

    \centering
    \caption{Elapsed Time Comparison with four series} \label{tab:time_4}
    \begin{tabular}{@{}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{}}
      \hline
      Package & Implementation & Elapsed Time(s) & Percentage Increase \\
      \hline
      Zebende & Zig (opt) & 35.88  & - \\
      Zebende & Zig (basic) & 59.74 & 52.7\% \\
      DCCA & Python & 447.67 &  1,243.49\% \\
      DCCA & R-Java & 2,206.3 & 6,126.17\% \\
      Zebende & Python & 3,076.23 & 8,542.83\% \\
      DFA & R & 28,818.016 & 80,049.42\% \\
      \hline
    \end{tabular}
  \end{table}

@@

      \centering
      \caption{Elapsed Time Comparison with twelve series} \label{tab:time_12}
      \begin{tabular}{@{}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{}}
        \hline
        Package & Implementation & Elapsed Time(s) & Percentage Increase \\
        \hline
        Zebende & Zig (opt) & 120.55  & - \\
        Zebende & Zig (basic) & 213.08 & 76.64\% \\
        Zebende & Python & 3,761.40 & 3,085.47\% \\
        DCCA & Python & 4,675.17 &  3,871.65\% \\
        DCCA & R-Java & 4,8624.44 & 40,423.52\% \\
        DFA & R & 2,060,776.24 & 81,704,499.33\% \\
        \hline
      \end{tabular}
    \end{table}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{
    figs/elapsed_tws.png}
  \caption{\label{fig:elapsed_tws}Elapsed Time Comparison for Different Implementations (four series)}
\end{figure}

@@

>>>>

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Fernando Ferraz Ribeiro~\orcidlink{0000-0002-0685-4774}\\Federal University of Bahia
   \And Gilney Figueira Zebende~\orcidlink{0000-0003-2420-9805}\\Universidade Estadual\\de Feira de Santana}
\Plainauthor{Fernando Ferraz Ribeiro, Gilney Figueira Zebende}
%  and $DMC_x^2$
%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$}
\Plaintitle{A Python/Zig optimized and customizable implementation for the Pdcca and DMCx2 methods}
\Shorttitle{\proglang{Python}/\proglang{Zig} implementation for the $\rho_{DCCA}$ and $DMC_x^2$}

@@

    \centering
    \caption{Elapsed Time Comparison with four series} \label{tab:time_4}
    \begin{tabular}{@{}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{}}
      \hline
      Package & Implementation & Elapsed Time(s) & Percentage Increase \\
      \hline
      Zebende & Zig (opt) & 35.88  & - \\
      Zebende & Zig (basic) & 59.74 & 66.50\% \\
      DCCA & Python & 447.67 &  1,147.69\% \\
      DCCA & R-Java & 2,206.2 & 6,048.83\% \\
      Zebende & Python & 3,076.23 & 8,473.66\% \\
      DFA & R & 28,116.00 & 78,261.20\% \\
      \hline
    \end{tabular}
  \end{table}

@@

      \centering
      \caption{Elapsed Time Comparison with twelve series} \label{tab:time_12}
      \begin{tabular}{@{}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{}}
        \hline
        Package & Implementation & Elapsed Time(s) & Percentage Increase \\
        \hline
        Zebende & Zig (opt) & 120.55  & - \\
        Zebende & Zig (basic) & 213.08 & 76.64\% \\
        Zebende & Python & 3,761.40 & 3,020.20\% \\
        DCCA & Python & 4,675.17 &  3,778.20\% \\
        DCCA & R-Java & 28,980.00 & 23,939.82\% \\
        DFA & R & 309,276.00 & 256,454.13\% \\
        \hline
      \end{tabular}
    \end{table}

@@

\begin{figure}[h!] 
  \centering
  \includegraphics{
    figs/elapsed_tws_04.png}
  \caption{\label{fig:elapsed_tws_04}Elapsed Time Comparison for Different Implementations (four time series)}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{
    figs/elapsed_tws_12.png}
  \caption{\label{fig:elapsed_tws_12}Elapsed Time Comparison for Different Implementations (twelve time series)}
\end{figure}
